---
output: html_document
---

## Statistical Inference: Course Project - Part One

# Investigation of the Exponential Distribution in R and Its Comparing with the Central Limit Theorem

Sagi Greenstine

## Overview

This report is a investigation of the Exponential Distribution, applied in R, and its comparison with the Central Limit Theorem statements. 
The Central Limit Theorem states that, given certain conditions, the arithmetic mean of a sufficiently large number of iterates of independent random variables, each with a well-defined expected value and well-defined variance, will be approximately normally distributed, regardless of the underlying distribution. 
For this comparison I'll investigate the distribution of averages of 40 exponentials, for receiving of large number of averages I'll do a thousand simulations.

## Simulations

For investigation of the Exponential Distribution must obtain a large number of averages of the exponential distributions of 40 observations. For this I'll create a matrix whose rows are the exponential distributions of 40 observations. In total, the matrix will contain thousand lines, in accordance with the number of simulations. The matrix will contain 40 columns in accordance with the number of observations for each distribution.
After receiving the matrix, I'll calculate the average of each line, and thus, it will be a distribution of the averages of the exponential distributions.

```{r runexpsimulation}
set.seed(10)
nosim <- 1000
n <- 40
lambda <- 0.2
expsim <- matrix(rexp(nosim*n, rate=lambda), nosim, n)
averages <- rowMeans(expsim)
```

Let's see the histogram of the distribution:

```{r sampleplot, echo=FALSE}
hist(averages, prob=TRUE, breaks=50, col="blue", main="Sample Distribution", xlab="Averages")
abline(v=mean(averages), lwd=3)
abline(v=1/lambda, col="red", lwd=3)
legend('topright', c("Sample mean", "Theoretical mean"), lty=c(1,1), col=c("black", "red"))
lines(density(averages), lwd=3)
```

## Sample Mean versus Theoretical Mean

Let's see the sample mean and compare it to the theoretical mean of the distribution.

The sample mean is equal to `r mean(averages)`.

The theoretical mean of exponential distribution is $1/\lambda$, i.e. `r 1/lambda`.

## Sample Variance versus Theoretical Variance

Let's see the sample variance and compare it to the theoretical variance of the distribution.

The sample variance is equal to `r var(averages)`.

The theoretical variance of exponential distribution is $\sigma^2 / n = 1/(\lambda^2 n) = 1/(0.04 \times 40)$ = `r 1/(0.04 * 40)`.

## Distribution

Let’s see the following figure that contains the histograms of the sample distribution and the normal distribution of the expected values:

```{r samplevsnormplot, echo=FALSE}
hist(averages, prob=TRUE, breaks=50, main="Sample Distribution versus Normal Distribution", xlab="Averages")
lines(density(averages), lwd=2, col="blue")
abline(v=mean(averages), col="blue", lwd=2)
xfit <- seq(min(averages), max(averages), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(n)))
abline(v=1/lambda, col="red", lty=2, lwd=2)
lines(xfit, yfit, col="red", lty=2, lwd=2)
legend('topright', c("Sample dist.", "Normal dist."), lty=c(1,2), col=c("blue", "red"))
```

We can see that the two distributions are very close, i.e. the sample distribution is approximately normal.

