
## Statistical Inference: Course Project - Part Two

# The "ToothGrowth"" Dataset Basic Inferential Analysis

Sagi Greenstine

## Overview

### The "ToothGrowth"" Dataset

The ToothGrowth dataset in R this is a set of observations of the effect of vitamin C on tooth growth in guinea pigs.

The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

Source: C. I. Bliss (1952) The Statistics of Bioassay. Academic Press.

### The Course Project Report

This report is a basic inferential analysis of the ToothGrowth data in the R datasets package. Firstly, I'll load the dataset and perform some basic exploratory analyses, it will also be presented a basic summary of the data. After that will be used confidence intervals and hypothesis tests to compare tooth growth by supp and dose. 

## Data Processing

### Loading and preprocessing the data

Loading the dataset:

```{r loaddata}
if(!exists("tgdata")){
  tgdata <- ToothGrowth
}
```

The structure of the data:

```{r strdataset}
str(tgdata)
```

A data frame with 60 observations on 3 variables:

1. **len**      *numeric*       - Tooth length

2. **supp**     *factor*        - Supplement type (VC or OJ)

3. **dose**	*numeric*       - Dose in milligrams/day

### 1. Load the ToothGrowth data and perform some basic exploratory data analyses

### 2. Provide a basic summary of the data.

### 3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

### 4. State your conclusions and the assumptions needed for your conclusions.
