
## Statistical Inference: Course Project - Part One

# Investigation of the Exponential Distribution in R and Its Comparing with the Central Limit Theorem

Sagi Greenstine

## Overview

This report is a investigation of the Exponential Distribution, applied in R, and its comparison with the Central Limit Theorem statements. 
The Central Limit Theorem states that, given certain conditions, the arithmetic mean of a sufficiently large number of iterates of independent random variables, each with a well-defined expected value and well-defined variance, will be approximately normally distributed, regardless of the underlying distribution. 
For this comparison I'll investigate the distribution of averages of 40 exponentials, for receiving of large number of averages I'll do a thousand simulations.

## Simulations

For investigation of the Exponential Distribution must obtain a large number of averages of the exponential distributions of 40 observations. For this I'll create a matrix whose rows are the exponential distributions of 40 observations. In total, the matrix will contain thousand lines, in accordance with the number of simulations. The matrix will contain 40 columns in accordance with the number of observations for each distribution.
After receiving the matrix, I'll calculate the average of each line, and thus, it will be a distribution of the averages of the exponential distributions.

```{r runexpsimulation}
set.seed(10)
nosim <- 1000
n <- 40
lambda <- 0.2
expsim <- matrix(rexp(nosim*n, rate=lambda), nosim, n)
averages <- rowMeans(expsim)
```

## Sample Mean versus Theoretical Mean

1. Show the sample mean and compare it to the theoretical mean of the distribution.

Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.

plot the histogram of averages

```{r compexpclt}
hist(averages, breaks=50, prob=TRUE,
     main="Distribution of averages of samples,
     drawn from exponential distribution with lambda=0.2",
     xlab="")
# density of the averages of samples
lines(density(averages))
# theoretical center of distribution
abline(v=1/lambda, col="red")
# theoretical density of the averages of samples
xfit <- seq(min(averages), max(averages), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(n)))
lines(xfit, yfit, pch=22, col="red", lty=2)
# add legend
legend('topright', c("simulation", "theoretical"), lty=c(1,2), col=c("black", "red"))
```

## Sample Variance versus Theoretical Variance

2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

## Distribution

3. Show that the distribution is approximately normal.
In point 3, focus on the difference between the distribution of a large collection of random exponentials and the distribution of a large collection of averages of 40 exponentials.

Via figures and text, explain how one can tell the distribution is approximately normal.

### Subtitle

```{r name}
  
```
