## Statistical Inference: Course Project - Part One

# Investigation of the Exponential Distribution in R and Its Comparing with the Central Limit Theorem

Sagi Greenstine

## Overview

In a few (2-3) sentences explain what is going to be reported on.

This report is a comparison of the Exponential Distribution, applied in R, with the Central Limit Theorem statements.


## Simulations

Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.

```{r runexpsimulation}
set.seed(3)
lambda <- 0.2
num_sim <- 1000
sample_size <- 40
sim <- matrix(rexp(num_sim*sample_size, rate=lambda), num_sim, sample_size)
row_means <- rowMeans(sim)
```

## Sample Mean versus Theoretical Mean

Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.

## Sample Variance versus Theoretical Variance

Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

## Distribution

Via figures and text, explain how one can tell the distribution is approximately normal.

### Subtitle

```{r name}
  
```
